Reduced plasticity and opportunity for selection in terrestrial ectotherm populations

### 2023-04-16 ms.qmd
I think we make predcitions using 'uncertainty' from sample_new_levels argument.

  # We'll now make the predcitions from the model object using the new dataframe
  terre_pred <- predict(model5_bayes, newdata = new_data_t2, summary = TRUE, allow_new_levels = TRUE, robust = FALSE)

  # Test manual calculations. We can also set summary = FALSE and then do the calculations ourselves. Note we want robust = FALSE to make the comparisons more similar as otherwise the calculation are different when using summary TRUE/FALSE  
  terre_pred2 <- predict(model5_bayes, newdata = new_data_t2, summary = FALSE, allow_new_levels = TRUE, robust = FALSE)
  plyr::ldply(apply(terre_pred2, 2, function(x) post_summary(x)))

>>>>

  # We'll now make the predcitions from the model object using the new dataframe
  terre_pred <- predict(model5_bayes, newdata = new_data_t2, summary = TRUE, allow_new_levels = TRUE, sample_new_levels = "uncertainty", robust = FALSE, intervals = "confidence")

  # Test manual calculations. We can also set summary = FALSE and then do the calculations ourselves. Note we want robust = FALSE to make the comparisons more similar as otherwise the calculation are different when using summary TRUE/FALSE  
  terre_pred2 <- predict(model5_bayes, newdata = new_data_t2, summary = FALSE, allow_new_levels = TRUE, sample_new_levels = "uncertainty", robust = FALSE)
  plyr::ldply(apply(terre_pred2, 2, function(x) post_summary(x)))
